Project Blog

### 2025-01-05 posts.qmd
Research blog moving

---
title: "Project Blog"
listing: 
  contents: posts # all Quarto docs in the `posts` directory will be included on your listing page
  type: grid # or `default` or `table`; each type has its own set of yaml options to include
  sort: 
      - "date-modified desc" # can also sort on more than one field
      - "date desc"
  categories: true # allows you to sort posts by assigned categories
  sort-ui: [date-modified, title]
  fields: [image, date-modified, title, description, date, author]
  page-size: 6
format:
  html:
    css: styles2.css
class: custom-font-pos
website:
  favicon: Virginia_Tech_seal.svg.png
  image: Horizontal_VT_Full_Color_RGB.png

  sidebar:
    tools:
      - icon: github
        href: https://github.com/Shaokang-Yang
      - icon: linkedin
        href: https://www.linkedin.com/in/shaokang-y-52b633162/
    section: true
    contents:
      - href: index.qmd
        text: Home
      - research.qmd
      - teaching.qmd
      - posts.qmd
---

>>>>

---
title: "Project Blog"

website:
  favicon: Virginia_Tech_seal.svg.png
  image: Horizontal_VT_Full_Color_RGB.png
  sidebar:
    tools:
      - icon: github
        href: https://github.com/Shaokang-Yang
      - icon: linkedin
        href: https://www.linkedin.com/in/shaokang-y-52b633162/
    section: true
    contents:
      - href: index.qmd
        text: Home
      - research.qmd
      - teaching.qmd
      - posts.qmd
---
